Competing Bandits

### 2018-08-10 analysis_code/agents_table.Rmd
update analysis

#dat <- read.csv(file=paste(WORKING_PATH, "/results/free_obs_raw_results/free_obs_experiment_tournament_raw_results.csv", sep=""))
#dat_3 <- read.csv(file=paste(WORKING_PATH, "/results/tournament_raw_results/tournament_experiment_large_horizon_3_raw.csv", sep=""))
#dat <- read.csv(file=paste(WORKING_PATH, "/results/tournament_raw_results/tournament_experiment_many_arms_haystack_raw.csv", sep=""))
#dat_2 <- read.csv(file=paste(WORKING_PATH, "/results/tournament_raw_results/tournament_experiment_many_arms_2_raw.csv", sep=""))
#dat_10 <- rbind(dat, dat_2)
dat <- read.csv(file=paste(WORKING_PATH, "/results/tournament_raw_results/tournament_experiment_ws_small_erase_rep_raw.csv", sep=""))
dat_3 <- dat

p1_algs <- as.list(unique(dat_3['P1.Alg']))$P1.Alg
p2_algs <- as.list(unique(dat_3['P2.Alg']))$P2.Alg
agent_algs <- as.list(unique(dat_3['Agent.Alg']))$Agent.Alg
time_horizons <-  as.list(unique(dat_3['Time.Horizon']))$Time.Horizon
time_horizons <- c(5000)
priors <- as.list(unique(dat_3['Prior']))$Prior
warm_starts <-  sort(as.list(unique(dat_3['Warm.Start']))$Warm.Start, decreasing=FALSE)

>>>>

#dat <- read.csv(file=paste(WORKING_PATH, "/results/free_obs_raw_results/free_obs_experiment_tournament_raw_results.csv", sep=""))
#dat_3 <- read.csv(file=paste(WORKING_PATH, "/results/tournament_raw_results/tournament_experiment_large_horizon_3_raw.csv", sep=""))
#dat <- read.csv(file=paste(WORKING_PATH, "/results/tournament_raw_results/tournament_experiment_many_arms_haystack_raw.csv", sep=""))
#dat_2 <- read.csv(file=paste(WORKING_PATH, "/results/tournament_raw_results/tournament_experiment_many_arms_2_raw.csv", sep=""))
#dat_10 <- rbind(dat, dat_2)
dat <- read.csv(file=paste(WORKING_PATH, "/results/tournament_raw_results/tournament_experiment_full_sim_with_realizations_raw.csv", sep=""))
dat_3 <- dat

p1_algs <- as.list(unique(dat_3['P1.Alg']))$P1.Alg
p2_algs <- as.list(unique(dat_3['P2.Alg']))$P2.Alg
agent_algs <- as.list(unique(dat_3['Agent.Alg']))$Agent.Alg
time_horizons <-  as.list(unique(dat_3['Time.Horizon']))$Time.Horizon
time_horizons <- c(2000)
priors <- as.list(unique(dat_3['Prior']))$Prior
warm_starts <-  sort(as.list(unique(dat_3['Warm.Start']))$Warm.Start, decreasing=FALSE)

### 2018-08-10 analysis_code/tournament_table.Rmd
update analysis

#dat <- read.csv(file=paste(WORKING_PATH, "/results/tournament_raw_results/tournament_experiment_parallel_test_raw.csv", sep=""))
dat <- read.csv(file=paste(WORKING_PATH, "/results/free_obs_raw_results/free_obs_experiment_free_obs_10_arms_raw.csv", sep=""))
p1_algs <- as.list(unique(dat['P1.Alg']))$P1.Alg
p2_algs <- as.list(unique(dat['P2.Alg']))$P2.Alg
agent_algs <- as.list(unique(dat['Agent.Alg']))$Agent.Alg
time_horizons <-  as.list(unique(dat['Time.Horizon']))$Time.Horizon
time_horizons <- c(5000)
priors <- as.list(unique(dat['Prior']))$Prior

ZERO_ONE_CUTOFF <- 0.1
algs <- c("ThompsonSampling", "DynamicEpsilonGreedy", "DynamicGreedy")
alg_names <- c("Thompson Sampling", "Dynamic Epsilon Greedy", " DynamicGreedy")
options(xtable.sanitize.text.function=identity)
options(xtable.caption.placement="top")
library(xtable)
for (j in 1:length(time_horizons)) {
  for (prior in priors) {
    for (i in 1:length(agent_algs)) {
      agent_alg <- agent_algs[i]
      print_breaks <- FALSE
        time <- time_horizons[j]
        results <- matrix(nrow=length(algs), ncol=length(algs))
        colnames(results) <- alg_names
        rownames(results) <- alg_names
        for (k in 1:length(algs)) {
          for (l in 1:length(algs)) {
            p1alg = algs[k]
            p2alg = algs[l]
            filtered_dat <- filter(dat, P1.Alg == p1alg & P2.Alg == p2alg & Warm.Start == 5 & Prior == prior & Agent.Alg == agent_alg & Time.Horizon == time)
            if (nrow(filtered_dat) == 0) {
              if (p1alg == p2alg) { print_breaks <- TRUE }
              next
            }
            share <- filtered_dat$Market.Share.for.P1
            test <- t.test(share)
            cin <- signif(test$conf.int[2] - mean(share), digits=2)
            shares <- sum(share >= (1 - ZERO_ONE_CUTOFF) | share <= ZERO_ONE_CUTOFF, na.rm=TRUE) / nrow(filtered_dat)
            cv_high <- qchisq(.975, df=length(share) - 1)
            cv_low <- qchisq(.025, df=length(share) - 1)
            lower_var <- signif((length(share) - 1) * var(share) / cv_high, digits=2)
            high_var <- signif((length(share) - 1) * var(share) / cv_low, digits=2)
            results[k, l] <- paste("<b>", signif(mean(share), digits=2), "</b> +/-", cin, "<br>", signif(var(share), digits=2), paste("(", lower_var, ", ", high_var, ")", sep=""), "<br>", "Extreme Shares:", 100*signif(shares, digits=2), "%")
          }
        }
        tab <-xtable(results, caption=paste("Results for", agent_alg, "t =", time, prior, "200 free obs", "K =", 10))
        print(tab, type="html")
        if (print_breaks) { print("<br>") }
      }
    }
  }

>>>>

dat <- read.csv(file=paste(WORKING_PATH, "/results/free_obs_raw_results/free_obs_experiment_testing_raw.csv", sep=""))
p1_algs <- as.list(unique(dat['P1.Alg']))$P1.Alg
p2_algs <- as.list(unique(dat['P2.Alg']))$P2.Alg
agent_algs <- as.list(unique(dat['Agent.Alg']))$Agent.Alg
time_horizons <-  as.list(unique(dat['Time.Horizon']))$Time.Horizon
time_horizons <- c(1000)
priors <- as.list(unique(dat['Prior']))$Prior

ZERO_ONE_CUTOFF <- 0.1
algs <- c("ThompsonSampling", "DynamicEpsilonGreedy", "DynamicGreedy")
alg_names <- c("Thompson Sampling", "Dynamic Epsilon Greedy", " DynamicGreedy")
options(xtable.sanitize.text.function=identity)
options(xtable.caption.placement="top")
library(xtable)
for (j in 1:length(time_horizons)) {
  for (prior in priors) {
    for (i in 1:length(agent_algs)) {
      agent_alg <- agent_algs[i]
      print_breaks <- FALSE
        time <- time_horizons[j]
        results <- matrix(nrow=length(algs), ncol=length(algs))
        colnames(results) <- alg_names
        rownames(results) <- alg_names
        for (k in 1:length(algs)) {
          for (l in 1:length(algs)) {
            p1alg = algs[k]
            p2alg = algs[l]
            filtered_dat <- filter(dat, P1.Alg == p1alg & P2.Alg == p2alg & Warm.Start == 20 & Prior == prior & Agent.Alg == agent_alg & Time.Horizon == time)
            if (nrow(filtered_dat) == 0) {
              if (p1alg == p2alg) { print_breaks <- TRUE }
              next
            }
            share <- filtered_dat$Market.Share.for.P1
            test <- t.test(share)
            cin <- signif(test$conf.int[2] - mean(share), digits=2)
            shares <- sum(share >= (1 - ZERO_ONE_CUTOFF) | share <= ZERO_ONE_CUTOFF, na.rm=TRUE) / nrow(filtered_dat)
            cv_high <- qchisq(.975, df=length(share) - 1)
            cv_low <- qchisq(.025, df=length(share) - 1)
            lower_var <- signif((length(share) - 1) * var(share) / cv_high, digits=2)
            high_var <- signif((length(share) - 1) * var(share) / cv_low, digits=2)
            results[k, l] <- paste("<b>", signif(mean(share), digits=2), "</b> +/-", cin, "<br>", signif(var(share), digits=2), paste("(", lower_var, ", ", high_var, ")", sep=""), "<br>", "Extreme Shares:", 100*signif(shares, digits=2), "%")
          }
        }
        tab <-xtable(results, caption=paste("Results for", agent_alg, "t =", time, prior, "200 free obs", "K =", 10))
        print(tab, type="html")
        if (print_breaks) { print("<br>") }
      }
    }
  }

### 2018-08-10 paper/competing_bandits.tex
update analysis

\begin{figure}
\caption{Relative Reputation Plots}
\includegraphics[scale=0.25]{"figures/deg_dg_ht_10_prelim"}
\includegraphics[scale=0.25]{"figures/ts_dg_ht_10_prelim"} \\
\includegraphics[scale=0.25]{"figures/deg_dg_nih_10_prelim"}
\includegraphics[scale=0.25]{"figures/ts_dg_nih_10_prelim"} \\
\caption*{\tiny{The plots contain the proportion of simulations over $250$ runs for a memory size of $100$ where, for a given $t$, the reputation of one algorithm is at least as high as the reputation of another on the same instance.}}
\label{relative_rep}
\end{figure}

@@

\begin{table}[ht]
\centering
\caption{Simultaneous Entry Needle In Haystack} 
\begin{tabular}{rlll}
  \hline
 & k = 20 & k = 100 & k = 200 \\ 
  \hline
TS vs DG & \makecell{\textbf{0.86} $\pm$0.02\\ eeog \\ avg: 14\\ med: 0} & \makecell{\textbf{0.65} $\pm$0.02\\ eeog \\ avg: 11\\ med: 0} & \makecell{\textbf{0.59} $\pm$0.02\\ eeog \\ avg: 6\\ med: 0} \\ 
  TS vs DEG & \makecell{\textbf{0.84} $\pm$0.02\\ eeog \\ avg: 20\\ med: 0} & \makecell{\textbf{0.62} $\pm$0.02\\ eeog \\ avg: 8\\ med: 0} & \makecell{\textbf{0.51} $\pm$0.03\\ eeog \\ avg: 5.4\\ med: 0} \\ 
  DG vs DEG & \makecell{\textbf{0.41} $\pm$0.02\\ eeog \\ avg: 400\\ med: 115} & \makecell{\textbf{0.47} $\pm$0.02\\ eeog \\ avg: 320\\ med: 0} & \makecell{\textbf{0.5} $\pm$0.02\\ eeog \\ avg: 290\\ med: 0} \\ 
   \hline
   \label{hm_nih}
\end{tabular}
\caption*{\tiny{The first line in each cell contains the average market share received by the firm playing Alg 1 (and the market share of Alg 2 is 1 - Alg 1 Market Share) as well as a 95 \% confidence band. For example, the cell in the top left indicates that TS gets on average 32\% of the market when played against DG. The next line contain the average and median effective end of game for this set of simulations.}}
\end{table}

\begin{table}[ht]
\centering
\caption{Simultaneous Entry Heavy Tail} 
\begin{tabular}{rlll}
  \hline
 & k = 20 & k = 100 & k = 200 \\ 
  \hline
TS vs DG & \makecell{\textbf{0.22} $\pm$0.02\\ eeog \\ avg: 0.27\\ med: 0} & \makecell{\textbf{0.41} $\pm$0.02\\ eeog \\ avg: 0.039\\ med: 0} & \makecell{\textbf{0.58} $\pm$0.02\\ eeog \\ avg: 12\\ med: 0} \\ 
  TS vs DEG & \makecell{\textbf{0.24} $\pm$0.02\\ eeog \\ avg: 3.2\\ med: 0} & \makecell{\textbf{0.48} $\pm$0.02\\ eeog \\ avg: 39\\ med: 0} & \makecell{\textbf{0.91} $\pm$0.01\\ eeog \\ avg: 84\\ med: 0} \\ 
  DG vs DEG & \makecell{\textbf{0.8} $\pm$0.02\\ eeog \\ avg: 16\\ med: 0} & \makecell{\textbf{0.86} $\pm$0.02\\ eeog \\ avg: 4.7\\ med: 0} & \makecell{\textbf{0.83} $\pm$0.02\\ eeog \\ avg: 2.7\\ med: 0} \\ 
   \hline
   \label{hm_ht}
\end{tabular}
\end{table}

>>>>

\begin{figure}
\caption{Relative Reputation Plots}
\includegraphics[scale=0.2]{"figures/deg_dg_ht_10_prelim"}
\includegraphics[scale=0.2]{"figures/ts_dg_ht_10_prelim"} \\
\includegraphics[scale=0.2]{"figures/deg_dg_nih_10_prelim"}
\includegraphics[scale=0.2]{"figures/ts_dg_nih_10_prelim"} \\
\caption*{\tiny{The plots contain the proportion of simulations over $250$ runs for a memory size of $100$ where, for a given $t$, the reputation of one algorithm is at least as high as the reputation of another on the same instance.}}
\label{relative_rep}
\end{figure}

@@

\begin{table}[ht]
\centering
\caption{Simultaneous Entry Needle In Haystack} 
\begin{tabular}{rlll}
  \hline
 & k = 20 & k = 100 & k = 200 \\ 
  \hline
TS vs DG & \makecell{\textbf{0.64} $\pm$0.03\\ eeog \\ avg: 210\\ med: 28} & \makecell{\textbf{0.62} $\pm$0.03\\ eeog \\ avg: 260\\ med: 68} & \makecell{\textbf{0.6} $\pm$0.03\\ eeog \\ avg: 320\\ med: 0} \\ 
  TS vs DEG & \makecell{\textbf{0.56} $\pm$0.03\\ eeog \\ avg: 150\\ med: 11} & \makecell{\textbf{0.54} $\pm$0.03\\ eeog \\ avg: 240\\ med: 24.5} & \makecell{\textbf{0.51} $\pm$0.03\\ eeog \\ avg: 420\\ med: 36.5} \\ 
  DG vs DEG & \makecell{\textbf{0.43} $\pm$0.03\\ eeog \\ avg: 330\\ med: 97.5} & \makecell{\textbf{0.42} $\pm$0.03\\ eeog \\ avg: 550\\ med: 229.5} & \makecell{\textbf{0.41} $\pm$0.02\\ eeog \\ avg: 650\\ med: 420} \\ 
   \hline
   \label{hm_nih}
\end{tabular}
\caption*{\tiny{The first line in each cell contains the average market share received by the firm playing Alg 1 (and the market share of Alg 2 is 1 - Alg 1 Market Share) as well as a 95 \% confidence band. For example, the cell in the top left indicates that TS gets on average 32\% of the market when played against DG. The next line contain the average and median effective end of game for this set of simulations.}}
\end{table}

\begin{table}[ht]
\centering
\caption{Simultaneous Entry Heavy Tail} 
\begin{tabular}{rlll}
  \hline
 & k = 20 & k = 100 & k = 200 \\ 
  \hline
TS vs DG & \makecell{\textbf{0.29} $\pm$0.03\\ eeog \\ avg: 65\\ med: 0} & \makecell{\textbf{0.52} $\pm$0.03\\ eeog \\ avg: 130\\ med: 0} & \makecell{\textbf{0.72} $\pm$0.02\\ eeog \\ avg: 500\\ med: 0} \\ 
  TS vs DEG & \makecell{\textbf{0.3} $\pm$0.03\\ eeog \\ avg: 26\\ med: 0} & \makecell{\textbf{0.59} $\pm$0.03\\ eeog \\ avg: 160\\ med: 0} & \makecell{\textbf{0.86} $\pm$0.02\\ eeog \\ avg: 420\\ med: 0} \\ 
  DG vs DEG & \makecell{\textbf{0.63} $\pm$0.03\\ eeog \\ avg: 390\\ med: 10} & \makecell{\textbf{0.62} $\pm$0.02\\ eeog \\ avg: 670\\ med: 500.5} & \makecell{\textbf{0.61} $\pm$0.02\\ eeog \\ avg: 770\\ med: 670.5} \\ 
   \hline
   \label{hm_ht}
\end{tabular}
\end{table}
